\documentclass[10pt,a4paper]{article}
\usepackage{amssymb,amsbsy,verbatim,fancybox,ifpdf}
\usepackage{graphicx}
\usepackage[usenames]{color}


\input{../ipc/macros.tex}

%% We must define this for the manual to operate correctly.
\newcommand{\showcommandline}[1]{
\begin{commandline}
\$ smc #1
\end{commandline}
}

\newcommand{\commandNameIpcSmc}{\smc}

%

\title{The \srmc\ Manual}
\author{
Allan Clark, Stephen Gilmore and Mirco Tribastone
}


\begin{document}
\maketitle



\section*{About \smc}

This document is a manual for users of the \srmc\ compiler.
Users are expected to already know how to interpret their models.
A companion document, "The \srmc\ tutorial" is available.
The tutorial explains how to use \srmc\ for stochastic modelling.

\section{Input and Output}
In this section we go over the input into the \srmc\ compiler and the
output from a normal run. In Section \ref{section:command-line-options}
the options to change the behaviour of the compiler are discussed.

\adcComment{Todo: explain tool chain}

\section{Command-line Usage}
\label{section:command-line-options}
\input{options.tex}

\section{Concrete Syntax}
\input{concreteSyntax}

\section{Notes, Comments and Questions}
\begin{itemize}
\item
There are three kinds of identifiers.
An upper-ident these begin with an upper-case letter and are used for
process names, eg $Client$.
A lower-ident these begin with a lower-case letter and are used for rate names,
eg $lambda$.
An all-upper-ident, these begin with and only contain upper-case letters though 
they may also have digits in them, eg $EDINBURGH$.
A qualified name, can end in any of the three kinds of identifiers, but it must
consist of a (possibly empty) chain of all-upper-idents followed
by double-colons, eg
$EDINBURGH::INFORMATICS::LFCS::Client$ is a qualified process name.
$EDINBURGH::INFORMATICS::LFCS::lambda$ is a qualified rate name.

\item
One may wish to combine the $conditional$ syntax for conditional behaviour and
functional rates. However the two te⟨st for distinct things. The first tests are
generally on rates and may be compiled out before the model is solved.
Functional rates on the other hand generally consist of process states and 
are a dynamic test which cannot be compiled out
(technically, cannot be evaluated at compile-time).

% \item
% Do we still wish to retain the legacy (optional) \# syntax
% to begin a process definition?
% The verdict seems to be yes.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\bibliographystyle{unsrt}
%\bibliography{../common/pepa}

\end{document}

